A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-11 paper.tex
Fix typesetting for consistency

\subsubsection{Time Complexity}
With given E2EE protocol framework. ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is O(n).\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is O(n), too. Therefore, the E2EE protocol framework takes only linear time. Applying mature cryptographic functions (e.g. SHA-256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.

>>>>

\subsubsection{Time Complexity}
With given E2EE protocol framework, ECDSA would take constant time under our situation, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too. Therefore, the E2EE protocol framework takes only linear time. Applying mature cryptographic functions (e.g. SHA-256, AES-CBC, etc) apparently makes E2EE perform with smaller slope.
